---
title: "Lab 10: Predicting house prices"
author: "MinJae Jo"
date: "`r Sys.Date()`"
output: 
  pdf_document:
    highlight: tango
    toc: false
    df_print: kable
    fig_caption: no
    number_sections: no
    dev: pdf
  html_document:
    highlight: tango
    self_contained: true
    theme: paper
    toc: no
    df_print: kable
    fig_caption: no
    number_sections: no
    smart: yes
    dev: svg
geometry: margin=1in
fontsize: 11pt
documentclass: article
---

```{r setup, include = FALSE}
# DO NOT ALTER CODE IN THIS CHUNK
# Set knitr options
knitr::opts_chunk$set(echo = TRUE)
# Load required packages
suppressPackageStartupMessages(library(tidyverse, quietly = TRUE))
suppressPackageStartupMessages(library(modelr))
suppressPackageStartupMessages(library(broom))
suppressPackageStartupMessages(library(lmvar))
# Load data
train <- read_csv("housing_train.csv")
test <- read_csv("housing_test.csv")
```

* * *

## Lab report
```{r}
str(train)
str(test)
```
## Exercises

#### Exercise 1
-The test loss was slightly higher than the training and validation losses, as the model had never encountered the test data before. The difference between the losses is small, so the model does not appear to be severely overfit.



#### Exercise 2
-Areas with high home prices are mostly concentrated in coastal areas, particularly Southern California and the Bay Area.



#### Exercise 3
i. Median_income showed the most pronounced relationship with house prices.

ii. House prices seem up to about half a million, but the value is cut, so the accuracy of linear models can decrease when predicting high values.


#### Exericse 4
-The category most concentrated in the lowest house price was INLAND.



#### Exericse 5
-The 5-fold validation RMSE of this model is about 84,000. In other words, when predicting a house price with just the median_income alone, there is an error of about $80,000 on average.



#### Exericse 6
-The cross-validation RMSE was much lower in the model created by adding all variables. Therefore, the prediction performance was clearly better than when using only media_income.



#### Exericse 7
