---
title: "Lab 3: Wrangling sales data"
author: "MinJae Jo"
date: "`r Sys.Date()`"
documentclass: article
geometry: margin=1in
fontsize: 11pt
output:
  pdf_document:
    highlight: tango
    toc: false
    df_print: tibble
    fig_caption: no
    number_sections: no
    dev: pdf
  html_document:
    highlight: tango
    self_contained: true
    theme: paper
    toc: no
    df_print: kable
    fig_caption: no
    number_sections: no
    smart: yes
    dev: svg
  github_document:
    html_preview: false
    toc: true
    toc_depth: 4
    dev: svg
    df_print: kable
---

```{r setup, include = FALSE}
# DO NOT ALTER CODE IN THIS CHUNK
# Set knitr options
knitr::opts_chunk$set(
  echo = TRUE, eval = TRUE, fig.width = 5,
  fig.asp = 0.618, out.width = "80%", dpi = 120,
  fig.align = "center", cache = FALSE
)

# Load packages
suppressPackageStartupMessages(library(tidyverse))

# Load dataset
coffeeshop <- read_csv("coffeeshop.csv")
coffeeshop$date <- as.Date(coffeeshop$date)
```



### Exercise 1

# i.
select(coffeeshop, !cogs)
#!cogs → Select all columns except for the cogs column

# ii.
select(coffeeshop, starts_with("prod"))
#Starts_with("prod") → product_line, select a column that begins with "prod", such as product

# iii.
select(coffeeshop, contains("pe"))
#contains("pe") → Select total_expenses column with "pe" in column name

# iv.
select(coffeeshop, caffeination = type)
#Recall and rename the correction = type → type column


### Exercise 2

```{r, echo=FALSE}
# i. coffeeshop
coffeeshop %>%
  select(caffeination = type)
```
```{r, echo=FALSE}
# ii. coffeeshop
coffeeshop %>%
  select(starts_with("prod")) %>%
  filter(product == "Darjeeling")
```



### Exercise 3




### Exercise 4





### Exercise 5




### Exercise 6





### Exercise 7