---
title: "Lab 5: Birth Ratios"
author: "Fill in your full name"
date: "`r Sys.Date()`"
documentclass: article
geometry: margin=1in
fontsize: 11pt
output:
  pdf_document:
    highlight: tango
    toc: false
    df_print: kable
    fig_caption: no
    number_sections: no
    dev: pdf
  html_document:
    highlight: tango
    self_contained: true
    theme: paper
    toc: no
    df_print: kable
    fig_caption: no
    number_sections: no
    smart: yes
    dev: svg
  github_document:
    html_preview: false
    toc: true
    toc_depth: 4
    dev: svg
    df_print: kable
---

```{r setup, include = FALSE}
# DO NOT ALTER CODE IN THIS CHUNK
# Set knitr options
knitr::opts_chunk$set(
  echo = TRUE, eval = TRUE, fig.width = 5,
  fig.asp = 0.618, out.width = "80%", dpi = 120,
  fig.align = "center", cache = FALSE
)
# Load packages
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(infer))
suppressPackageStartupMessages(library(HistData))
set.seed(42)
```

---

## Visualizing and quantifying the distribution

### Exercise 1




### Exercise 2
```{r, echo=FALSE, warning=FALSE}
library(ggplot2)
library(dplyr)
library(HistData)

data("Arbuthnot")

Arbuthnot_clean <- Arbuthnot |> distinct(Year, .keep_all = TRUE) |>
  mutate(Ratio = Males / Females)
ggplot(data = Arbuthnot_clean) +
  geom_boxplot(aes(x = "", y = Ratio)) +
  coord_flip() +
  labs(title = "Arbuthnot birth ratio (Males/Females): Boxplot",
       x = NULL, y = "Ratio")
ggplot(data = Arbuthnot_clean, aes(x = Ratio, y = ..density..)) +
  geom_histogram(binwidth = 0.01, color = "white") +
  labs(title = "Arbuthnot birth ratio (Males/Females): PMF",
       x = "Ratio", y = "Probability density")
```


### Exercise 3

```{r, echo=FALSE, warning=FALSE}
ggplot(data = Arbuthnot_clean, aes(x = Ratio, y = after_stat(density))) +
geom_histogram(binwidth = 0.01, fill = "lightblue", color = "white", alpha = 0.6) +
geom_density(color = "red", linewidth = 1) +
labs(
title = "Arbuthnot birth ratio (Males/Females): PMF + Density",
x = "Ratio",
y = "Probability density"
)

```

### Exercise 4
```{r, echo=FALSE, warning=FALSE}
Arbuthnot_clean %>%
summarize(
mean = mean(Ratio),
median = median(Ratio),
sd = sd(Ratio),
iqr = IQR(Ratio),
min = min(Ratio),
max = max(Ratio)
)

```

## `infer`ing a trend
```{r, echo=FALSE, warning=FALSE}
if(!require(infer)){
install.packages("infer")
}
library(infer)
```

### Exercise 5
```{r, echo=FALSE, warning=FALSE}
Arbuthnot_null <- Arbuthnot_clean %>%
specify(formula = Ratio ~ NULL) %>%
hypothesize(null = "point", mu = 1) %>%
generate(reps = 10000, type = "bootstrap") %>%
calculate(stat = "mean")

Arbuthnot_obs_stat <- Arbuthnot_clean %>%
specify(Ratio ~ NULL) %>%
calculate(stat = "mean")

Arbuthnot_null %>%
get_p_value(obs_stat = Arbuthnot_obs_stat, direction = "two_sided")

Arbuthnot_null %>%
visualize() +
shade_p_value(obs_stat = Arbuthnot_obs_stat, direction = "two_sided")
```
-The null hypothesis assumes that the average ratio of male to female births is 1, meaning there’s no real difference between them. The alternative hypothesis suggests that the ratio is not exactly 1. Because this is a two-sided test, both higher and lower differences are considered. If the p-value ends up being less than 0.05, we reject the null hypothesis and say that the difference between male and female birth ratios is statistically significant.

### Exercise 6