---
title: "Lab 11: Databases"
author: "MinJae Jo"
date: "`r Sys.Date()`"
output: 
  pdf_document:
    highlight: tango
    toc: false
    df_print: kable
    fig_caption: no
    number_sections: no
    dev: pdf
geometry: margin=1in
fontsize: 11pt
documentclass: article
---

```{r setup, include = FALSE}
# DO NOT ALTER THIS CHUNK
knitr::opts_chunk$set(
  echo = TRUE,
  eval = TRUE,
  fig.width = 5,
  fig.asp = 0.618,
  out.width = "70%",
  dpi = 120,
  fig.align = "center",
  cache = FALSE
)

suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(dbplyr))
suppressPackageStartupMessages(library(RSQLite))
if(file.exists("nycflights13.sqlite") == FALSE){
  dbplyr::nycflights13_sqlite(path = ".")
}
```


## Lab report

### Exercise 1
```{r}
library(DBI)
library(RSQLite)
library(dbplyr)

con <- dbConnect(SQLite(), "nycflights13.sqlite")
```


### Exercise 2
```{r}
library(dbplyr)
flights_tbl <- tbl(con, "flights")
```

### Exercise 3
```{r}
flights_query <- flights_tbl %>%
  select(year, month, day, hour, dep_delay, origin)
```

### Exercise 4
```{r,echo=FALSE}
show_query(flights_query)
```

### Exercise 5
```{r}
flights_df <- flights_query %>%
  collect()
```

### Exercise 6
```{r, echo=FALSE}
library(ggplot2)
ggplot(flights_df, aes(x = dep_delay)) +
  geom_histogram(binwidth = 5, color = "white") +
  labs(title = "Distribution of Departure Delays",
       x = "Departure Delay (minutes)",
       y = "Count")
```
- The average is much higher than the median, meaning there are many very long delays that drive the average up. While most flights don't experience significant delays, some have very long delays.

### Exercise 7
i. Each row represents a weather observation record of a specific date and time at an airport in one of the JFK/LGA/EWRs.

ii. The precip column contains information related to rain or precipitation.

iii. The origin column indicates at which airport (JFK, LGA, EWR) the meteorological measurements were made.


### Exercise 8
```{r, echo=FALSE}
weather_tbl <- tbl(con, "weather")

weather_query <- weather_tbl %>%
  select(origin, year, month, day, hour, temp, wind_speed, precip)

show_query(weather_query)
```


### Exercise 9
```{r, echo=FALSE}
joined_query <- flights_query %>%
  left_join(weather_query,
            by = c("origin", "year", "month", "day", "hour"))

show_query(joined_query)
```


### Exercise 10



### Exercise 11



### Exercise 12
